Weight-adjusted discontinuous Galerkin methods: matrix-valued weights and elastic wave propagation in heterogeneous media

### 2019-09-06 docs/ESDG_mortar/main.tex
updating docs

%\date{}
\author{Jesse Chan, David C.\ Del Rey Fernandez}
\title{Mortar-based entropy stable modal discontinuous Galerkin methods}
\graphicspath{{./figs/}}

@@

\begin{abstract}
Entropy stable schemes provide a semi-discrete statement of stability for nonlinear systems of conservation laws.  Entropy stable nodal discontinuous Galerkin (DG) methods have been constructed using entropy conservative finite volume fluxes \cite{tadmor1987numerical} and a summation-by-parts (SBP) finite difference framework \cite{gassner2013skew, carpenter2014entropy, gassner2016split, chen2017entropy, crean2018entropy, chan2017discretely, chan2018efficient}.  Such DG schemes require evaluating entropy conservative numerical fluxes between combinations of volume and surface quadrature nodes.  
\end{abstract}

@@

We incorporate mortars by modifying this formulation.  Let $\bm{V}_m$ denote the matrix which maps volume quadrature points to values at surface \textit{mortar} points.  We also need to introduce interpolation operators $\bm{T}_f, \bm{T}_m$ for surface trace spaces.  Here, $\bm{T}_f$ maps from polynomials on the surface $\partial \hat{D}$ to surface quadrature points, while $\bm{T}_m$ maps from polynomials on $\partial \hat{D}$ to mortar quadrature points.  We can then define surface and mortar mass and projection matrices
\begin{align*}
\bm{M}_m = \bm{T}_m^T\bm{W}_m\bm{T}_m, \qquad \bm{P}_m = \bm{M}_m^{-1}\bm{T}_m^T\bm{W}_m\\
\bm{M}_f = \bm{T}_f^T\bm{W}_f\bm{T}_f, \qquad \bm{P}_f = \bm{M}_m^{-1}\bm{T}_f^T\bm{W}_f.
\end{align*}
Note that we have used the mortar mass matrix $\bm{M}_m$ in the above definition of the face projection.  This is only necessary if the surface and mortar quadratures do not exactly integrate degree $2N$ polynomials.  If both the surface and mortar quadratures are exact for polynomials of degree $2N$, then $\bm{M}_m = \bm{M}_f$, and no distinction is necessary between the two mass matrices.

>>>>

%\date{}
\author{Jesse Chan, Mario Bencomo, David C.\ Del Rey Fernandez}
\title{On mortar-based entropy stable modal discontinuous Galerkin methods}
\graphicspath{{./figs/}}

@@

\begin{abstract}
Entropy stable schemes provide a semi-discrete statement of stability for nonlinear conservation laws.  Entropy stable nodal discontinuous Galerkin (DG) methods have been constructed using entropy conservative finite volume fluxes \cite{tadmor1987numerical} and a summation-by-parts (SBP) finite difference framework \cite{gassner2013skew, carpenter2014entropy, gassner2016split, chen2017entropy, crean2018entropy, chan2017discretely, chan2018efficient}.  Entropy stable DG schemes require evaluating entropy conservative numerical fluxes between combinations of volume and surface quadrature nodes.  On tensor product elements with surface nodes aligned with volume nodes, flux evaluations are required only between ``lines'' of nodes, reducing the number of flux evaluations to $O(N)$ per node.  However, because surface nodes are no longer aligned on non-conforming meshes, each volume node interacts each non-aligned surface node, increasing the number of flux evaluations to $O(N^{d-1})$ per node in $d$ dimensions.  
\end{abstract}

@@

We incorporate mortars by modifying this formulation.  Let $\bm{V}_m$ denote the matrix which maps volume quadrature points to values at surface \textit{mortar} points.  We also need to introduce interpolation operators $\bm{T}_f, \bm{T}_m$ for surface trace spaces.  Here, $\bm{T}_f$ maps from polynomials on the surface $\partial \hat{D}$ to surface quadrature points, while $\bm{T}_m$ maps from polynomials on $\partial \hat{D}$ to mortar quadrature points.  We can then define surface and mortar mass and projection matrices
\begin{align*}
\bm{M}_m = \bm{T}_m^T\bm{W}_m\bm{T}_m, \qquad \bm{P}_m = \bm{M}_m^{-1}\bm{T}_m^T\bm{W}_m\\
\bm{M}_f = \bm{T}_f^T\bm{W}_f\bm{T}_f, \qquad \bm{P}_f = \bm{M}_m^{-1}\bm{T}_f^T\bm{W}_f.
\end{align*}
Note that we have used the mortar mass matrix $\bm{M}_m$ in the above definition of the face projection.  %This is only necessary if the surface and mortar quadratures do not exactly integrate degree $2N$ polynomials.  If both the surface and mortar quadratures are exact for polynomials of degree $2N$, then $\bm{M}_m = \bm{M}_f$, and no distinction is necessary between the two mass matrices.

### 2019-09-06 docs/elasticity_notes/arxiv/main.tex
updating docs for penalty note + elasticity
updating docs

%\newcommand{\cond}[1]{\kappa\LRp{#1}}
%\newcommand{\cond}[2]{\nor{#1}_{#2}\nor{{#1}^{-1}}_{#2}}

@@

&\leq \frac{1}{2}\sum_{D^k\in \Oh}\nor{\avg{\bm{\epsilon}_\sigma} - \frac{\tau_v}{2}\bm{A}_n\jump{\bm{\epsilon}_v}}_{\Ldk} \nor{\bm{A}_n\jump{\bm{\eta}_v}}_{\Ldk} + \nor{\avg{\bm{\epsilon}_v} - \frac{\tau_\sigma}{2}\bm{A}_n^T\jump{\bm{\epsilon}_\sigma}}_{\Ldk}\nor{\bm{A}_n^T\jump{\bm{\eta}_{\sigma}}}_{\Ldk}\\ 

@@

In all experiments, we follow \cite{chan2016weight1} and compute application of weight-adjusted mass matrices using a quadrature exact for polynomials of degree $(2N+1)$ \cite{xiao2010quadrature}.  Time integration is performed using the low-storage 4th order five-stage Runge-Kutta scheme of Carpenter and Kennedy \cite{carpenter1994fourth}, and the time-step is chosen based on the global restriction
\[
dt = \min_{k} \frac{C_{\rm CFL}}{  \sup_{\bm{x}\in\Omega}\nor{\bm{C}(\bm{x})}_{2} C_N \nor{J^f}_{L^{\infty}\LRp{\partial D^k}}\nor{J^{-1}}_{L^{\infty}\LRp{D^k}}}
\]
where $C_N = O(N^2)$ is the order-dependent constant in the surface polynomial trace inequality \cite{chan2015gpu} and $C_{\rm CFL}$ is a tunable global CFL constant.  Finally, in all following experiments, we use $\tau_v = \tau_\sigma = 1$ unless specified otherwise.

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{loglogaxis}[
	legend cell align=left,
	width=.49\textwidth,
    xlabel={Mesh size $h$},
       ylabel={$L^2$ errors}, 
    xmin=.025, xmax=1,
    ymin=1e-12, ymax=1,
    legend pos=south east,
    xmajorgrids=true,
    ymajorgrids=true,
    grid style=dashed,
]

>>>>

%\newcommand{\cond}[1]{\kappa\LRp{#1}}
\newcommand{\cond}[2]{\nor{#1}_{#2}\nor{{#1}^{-1}}_{#2}}

@@

&\leq \frac{1}{2}\sum_{D^k\in \Oh}\nor{\avg{\bm{\epsilon}_\sigma} - \frac{\tau_v}{2}\bm{A}_n\jump{\bm{\epsilon}_v}}_{\Ldk} \nor{\bm{A}_n\jump{\bm{\eta}_v}}_{\Ldk} \\
&\hspace{10em} + \nor{\avg{\bm{\epsilon}_v} - \frac{\tau_\sigma}{2}\bm{A}_n^T\jump{\bm{\epsilon}_\sigma}}_{\Ldk}\nor{\bm{A}_n^T\jump{\bm{\eta}_{\sigma}}}_{\Ldk}\\ 

@@

In all experiments, we follow \cite{chan2016weight1} and compute application of weight-adjusted mass matrices using a quadrature exact for polynomials of degree $(2N+1)$ \cite{xiao2010quadrature}.  Time integration is performed using the low-storage 4th order five-stage Runge-Kutta scheme of Carpenter and Kennedy \cite{carpenter1994fourth}, and the time-step is chosen based on the global restriction
\[
dt = \min_{k} \frac{C_{\rm CFL}}{  \sup_{\bm{x}\in\Omega}\nor{\bm{C}(\bm{x})}_{2} C_N \nor{J^f}_{L^{\infty}\LRp{\partial D^k}}\nor{J^{-1}}_{L^{\infty}\LRp{D^k}}}
\]
where $C_N = O(N^2)$ is the order-dependent constant in the surface polynomial trace inequality \cite{chan2015gpu} and $C_{\rm CFL}$ is a tunable global CFL constant.  Finally, in all following experiments, we use $C_{\rm CFL} = 1$ and $\tau_v = \tau_\sigma = 1$ unless specified otherwise.

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{loglogaxis}[
	legend cell align=left,
    legend pos=south east,
	width=.49\textwidth,
    xlabel={Mesh size $h$},
       ylabel={$L^2$ errors}, 
    xmin=.025, xmax=1,
    ymin=1e-12, ymax=1,
    xmajorgrids=true,
    ymajorgrids=true,
    grid style=dashed,
]
